%----------------------------------------------------------------------------------------
%   DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%   PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}    
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{supertabular}
\usepackage{titlesec}               
\usepackage{multicol}
\usepackage{multirow}
\usepackage{fontawesome5}
\usepackage[unicode, draft=false]{hyperref}

% Centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

% Section formatting
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

% Colors
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

% Job listing environment (Used for consistency)
\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

%----------------------------------------------------------------------------------------
%   BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%   TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Miles Zelasko} \\[7.5pt]
\href{https://linkedin.com/in/miles-zelasko}{\raisebox{-0.05\height}\faLinkedin\ miles-zelasko} \ $|$ \ 
\color{linkcolour}{\raisebox{-0.05\height}\faMapMarker\ South Portland, ME} \ $|$ \
\href{mailto:miles.zelasko@unh.edu}{\raisebox{-0.05\height}\faEnvelope \ miles.zelasko@unh.edu} \ $|$ \ 
\href{tel:2076325840}{\raisebox{-0.05\height}\faMobile \ (207) 632-5840} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%   EDUCATION (Moved to top - Critical for Engineering Students)
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{Bachelor of Science in Mechanical Engineering} & \hfill & Aug 2023 -- May 2027 \\
\textit{University of New Hampshire} & & \\[3.75pt]
\end{tabularx}
\begin{minipage}[t]{\linewidth}
\begin{itemize}[nosep, after=\strut, leftmargin=1em, itemsep=3pt, label=--]
    \item \textbf{Cumulative GPA:} 3.4/4.0
    \item \textbf{Relevant Coursework:} Thermal System Analysis and Design, Heat Transfer, Systems Modeling, Machine Design
\end{itemize}
\end{minipage}

%----------------------------------------------------------------------------------------
%   SKILLS (Moved up - Engineering scanners look for Solidworks/MATLAB early)
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Software} & SolidWorks, Visual Studio Code, Microsoft Office Suite \\
\textbf{Certifications} & SOLIDWORKS Associate (CSWA: C-LXSEG32AYR) \\
\textbf{Programming} & MATLAB, Python, Julia, Lua \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%   PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}
\begin{joblong}{Rock Climbing Training Tool}{June 2024 -- June 2025}
    \item Developed a training tool utilizing SolidWorks to increase finger strength, incorporating feedback from diverse skill levels.
    \item Prototyped and tested multiple iterations, achieving a $>50\%$ weight reduction and $43\%$ manufacturing cost decrease.
\end{joblong}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}
\begin{joblong}{Portland Discovery Land \& Sea Tours}{June 2021 -- August 2024}
    \item Managed sales and boarding logistics for over 500 daily customers, ensuring operational efficiency.
    \item Trained team members on point-of-sale systems and administrative procedures.
    \item Supported back-office operations and internal administrative telecommunications.
\end{joblong}

%----------------------------------------------------------------------------------------
%   EXTRACURRICULAR ACTIVITIES
%----------------------------------------------------------------------------------------
\section{Extracurricular Activities}
\begin{joblong}{RL$\mathbf{^2}$ (Reinforcement Learning Group)}{Sept 2025 -- Present}
    \item Participated in graduate-level reading groups focused on literature regarding sequential decision making.
    \item Gained familiarity with foundational concepts in dynamic programming and reinforcement learning.
\end{joblong}

\begin{joblong}{American Society of Mechanical Engineers (ASME)}{Sept 2023 -- Present}
    \item Engaged with industry experts regarding emerging trends and career development in Mechanical Engineering.
\end{joblong}

\end{document}
